---
title: "STAT295 Homework 1"
author: "Başak Uğurlu,Damla Başarmış,Zeynep Fenercioğlu"
date: "2024-04-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Q1

#### i.Reading the Data

```{r}
# wget https://raw.githubusercontent.com/dhavalpotdar/College-Scorecard-Data-Analysis/master/MERGED_2017_2018_cleaned.csv
```

#### Change the Name

```{r}
# mv MERGED_2017_2018_cleaned.csv college_score.csv 
```

#### Print the Lines 10 Through 60

```{r}
# head -n 60 college_score.csv | tail -n +10
```

#### ii.Create a sub-sample of the data set with the following condition: control = Public and city = Montgomery. Add this sub-sample to subsample.csv file.

```{r}
# awk -F, 'NR==1 || ($2=="Public" && $4=="Montgomery")' college_score.csv > subsample.csv
```

#### iii.Obtain the frequencies of each cities.

```{r}
#cut -d, -f3 college_score.csv | sort | uniq -c
```

### Q2

#### i.

```{r}
chocolate<-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv")
head(chocolate,6)
str(chocolate)
```

#### There are 2530 observations of 10 variables and it contains int,chr,num.

#### ii.

```{r}
library(dplyr)
chocolate_factor<-chocolate%>%
  mutate_all(as.factor)

```

#### iii.

```{r}
chocolate_summary<-chocolate%>%
  na.omit()%>%
  group_by(company_location)%>%
  summarize(
    Mean=mean(rating),
    Sd=sd(rating),
    Median=median(rating),
    range=max(rating)-min(rating)
  )
head(chocolate_summary,10)
```

#### Chile has the most mean value and Belgium has least mean value.Chile's variables are same because standard deviation and range values are 0

#### iv.

```{r}
q4<-chocolate %>% 
  subset(country_of_bean_origin=='Colombia' & review_date==2020)
head(q4)
```

#### v.

```{r}
chocolate%>%
  aggregate(cbind(rating, as.numeric(gsub("%", "", cocoa_percent))) ~ company_location,., mean)

```

#### vi.

```{r}
q6<-chocolate%>%
  select(company_manufacturer,company_location,country_of_bean_origin)
head(q6,10)  

```

#### vii.

```{r}
q7<-chocolate%>%
  filter(company_location=='Switzerland',rating>=3.25,rating<=3.5)
head(q7)
```

#### viii.

```{r}
chocolate%>%
  aggregate(rating~company_location,.,mean)%>%
  arrange(desc(rating))
```

#### ix.

```{r}
chocolate%>%
  group_by(country_of_bean_origin)%>%
  filter(company_manufacturer=='Bonnat')%>%
  count()
```

#### x.

```{r}
chocolate %>%
  mutate(
    Rating_Percentage=rating*25,
    Class=ifelse(Rating_Percentage<25,"Low",
                 ifelse(Rating_Percentage>=25 & Rating_Percentage<50,"Medium",
                        ifelse(Rating_Percentage>=50 & Rating_Percentage<=87.5,"Tasty",
                               "Excellent")))
  ) %>% head()
```

### Q3

```{r q3,include=FALSE}
library(tidyverse)
library(ggplot2)
```

### i.Reading the data and plotting with facet_wrap

```{r 1,warning=FALSE}
nmmaps<-read.csv("https://www.cedricscherer.com/data/chicago-nmmaps-custom.csv")
head(nmmaps)       
str(nmmaps)
nmmaps <- nmmaps |> 
  mutate(date = as.Date(date, format = "%Y-%m-%d"))
ggplot(data=nmmaps,aes(x=date,y=temp)) +
  geom_point(alpha=0.5)+
  facet_wrap(~year,scales="free")+
  labs(x = "Date", y = "Temperature", title = "Temperature by Year")+
  scale_x_date(date_labels = "%b", date_breaks = "1 month")+
  scale_y_continuous(limits = c(min(nmmaps$temp), max(nmmaps$temp)))
```

Interpretation: We see that in 1999, there were hotter days in summer compared to other years; in 2000, the temperature was cooler between November- January. In 1997 and 1999 temperature goes down below 0.

### ii.Examining the relationship using geom_point

```{r 2}
nmmaps$season <- factor(nmmaps$season, levels = c("Winter", "Spring", "Summer", "Autumn"))
season_colors <- c("Winter" = "lightblue",   
                   "Spring" = "lightgreen",  
                   "Summer" = "yellow", 
                   "Autumn" = "orange") 
ggplot(nmmaps, aes(x = date, y = temp, color = season)) +
  geom_point(alpha = 0.5) +
  labs(x = "Date", y = "Temperature", color = "Season", title = "Temperature by Season")+
  scale_color_manual(values = season_colors)
```

Interpretation: We see that it gets colder in autumn, and hotter in winter as time passes. We again see that in 1999, there were hotter days in summer compared to other years.

### iii. Relationship between temp and dewpoint

```{r 3}
correlation <- cor(nmmaps$temp, nmmaps$dewpoint)
rounded_cor <-round(correlation,3)
print(paste("Correlation coefficient between temperature and dewpoint:", rounded_cor))
ggplot(nmmaps, aes(x = temp, y = dewpoint)) +
  geom_point(alpha = 0.5) +
  labs(x = "Temperature", y = "Dew Point", title = "Temperature & Dew Point")
```

Interpretation: As we see from the plot and the correlation coefficient we just calculated as 0.958, there is a strong positive correlation between temperature and dew point since 0.958 is close to 1 and the plot is linear.

### Q4

```{r q4,include=FALSE}
libraries <- c("ggplot2","sf","rworldmap","tidyverse","magrittr",
               "leaflet", "dplyr", "rvest", "xml2",
               "maps","mapdata","RgoogleMaps","lubridate","rnaturalearth","dplyr","rnaturalearthdata","RColorBrewer","httr")
lapply(libraries, require, character.only = TRUE)

```

```{r map}
url <- "https://ds.iris.edu/seismon/eventlist/index.phtml"

res <- GET(url)
html_con <- content(res, "text")
html_ulke <- read_html(html_con)

tables <- html_ulke |> 
  html_nodes("table") |> 
  html_table() 
earthquake <- as.data.frame(tables)
str(earthquake)
earthquake %<>%
  mutate(Class = ifelse(MAG < 4.5, "Minor",
                        ifelse(MAG < 5.5, "Moderate", "Major")))
color_vector <- colorFactor(c("Yellow", "Blue", "Red"),
                            domain = earthquake$Class)
earthquake |> 
  leaflet() |> 
  addTiles() |> 
  addCircles(~LON, ~LAT,
             weight = 10,
             radius = 90,
             popup = paste0(
               "<b>Date: </b>",
               earthquake$DATE.and.TIME..UTC.,
               "<br>",
               "<b>Place: </b>",
               earthquake$ LOCATION................................Shows.interactive.map.,
               "<br>",
               "<b>Depth in km: </b>",
               earthquake$DEPTHkm,
               "<br>",
               "<b>Magnitude: </b>",
               earthquake$MAG),
             label = ~LOCATION................................Shows.interactive.map.,
             color = ~color_vector(Class)) |> 
  setView(lng = median(earthquake$LON),
          lat = median(earthquake$LAT),
          zoom = 2)
```
